---
title: "assignment_2"
author: "joshna katta"
date: "2022-10-19"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r}
library(lpSolve)
```

```{r}
Problem <- matrix(c(22,14,30,600,100,
                16,20,24,625,120,
                80,60,70,"-","-"),ncol = 5,byrow = TRUE)
colnames(Problem)<- c("Warehouse1","Warehouse2","Warehouse3","Production Cost","Production Capacity")
rownames(Problem)<-c("Plant A","Plant B","Monthly Demand")
Problem <-as.table(Problem)
Problem
```
```{r}
# Since production and demand is unbalanced, Dummy column is created
#
# Name of the column and rows:
costs <- matrix(c(622,614,630,0,
                  641,645,649,0),ncol = 4,byrow = TRUE)
colnames(costs)<- c("Warehouse1","Warehouse2","Warehouse3","Dummy")
rownames(costs)<-c("Plant A","Plant B")
costs <-as.table(costs)
costs
# Setting up the row signs and production capacity values
row.signs <- rep("<=",2)
row.rhs<- c(100,120)
# Setting up the column sign and demand values
col.signs <- rep(">=",4)
col.rhs <- c(80,60,70,10)
```

```{r}
# Running lptrans to find minimum cost
lptrans <- lp.transport(costs,"min",row.signs,row.rhs,col.signs,col.rhs)
# Values of all variables
lptrans$solution
```

```{r}
# Objective function 
lptrans$objval
```
# Therefore 

# x12 = 60

# x13 = 40

# x21 = 80

# x23 = 30

# Objective function is 132790.
$$ 2. \hspace{.2cm} formulate \hspace{.2cm} the\hspace{.2cm}  transportation\hspace{.2cm}  problem.$$


#Since the primal was to be minimized so that the transportation cost the dual of it would be to maximize the value added(VA).

$$ \text{Maximize VA} \hspace{.2cm}= 80 W_{1} +60 W_{2} +70W_{3}- 100P_{A}- 120P_{B}$$
$$Subject\hspace{.2cm}  to \hspace{.2cm} the \hspace{.2cm} following\hspace{.2cm}  constraints $$


$$ \ Total \hspace{.2cm} Profit \hspace{.2cm} Constraints$$


$$MR_{1} - MC_{1} \ge = 622$$
$$MR_{2} - MC_{1} \ge = 614$$
$$MR_{3} - MC_{1} \ge = 630$$
$$MR_{1} - MC_{2} \ge = 641$$
$$MR_{2} - MC_{2} \ge = 645$$
$$MR_{3} - MC{2} \ge = 649$$
$$Where\hspace{.2cm} MR_{1} = Marginal\hspace{.2cm} Revenue\hspace{.2cm}from\hspace{.2cm} Warehouse 1$$
$$MR_{2} = Marginal\hspace{.2cm}Revenue\hspace{.2cm} from\hspace{.2cm}Warehouse 2$$
$$MR_{3} = Marginal\hspace{.2cm} Revenue\hspace{.2cm} from\hspace{.2cm}Warehouse 3$$
$$MC_{1} = Marginal\hspace{.2cm} Cost\hspace{.2cm} from\hspace{.2cm}Plant 1$$
$$MC_{2} = Marginal\hspace{.2cm} Cost\hspace{.2cm} from\hspace{.2cm}Plant 2$$




$$3.\hspace{.2cm}Economic\hspace{.2cm} Interpretation\hspace{.2cm} of\hspace{.2cm} the\hspace{.2cm} dual$$
#Reduced production and shipping costs are the aim of AED's business.
#In order to accomplish this, the company will need to employ a logistics firm to handle the transportation, which will involve buying the AEDs and shipping them to multiple warehouses in an effort to cut the cost of production and shipping overall.

$$MR_{1} <= MC_{1} + 622$$
$$MR_{2} <= MC_{1} + 614$$
$$MR_{3} <= MC_{1} + 630$$
$$MR_{1} <= MC_{2} + 641$$
$$MR_{2} <= MC_{2} + 645$$
$$MR_{3} <= MC_{2} + 649$$


$$MR_{1} <= MC_{1} + 621\hspace{.4cm}i.e.\hspace{.4cm} MR_{1} >= MC_{1}$$
#"Based on above interpretation,we can conclude that,profit maximization takes place if MC is equal to MR." 










